Correctly Optimizing Abstract Abstract Machines

### 2013-03-29 paper/paper.tex
Better wording of first theorem.

\begin{theorem}
Timestamps are a complete abstraction.
\end{theorem}
The proof follows from the Galois connection that, in one direction,
sorts all the stores in $S$ to form $\Sigma$, and translates stores in
$S$ to their distance from the end of $\Sigma$. In the other
direction, timestamps are replaced by the stores they point to.

>>>>

\begin{theorem}
$\widehat{\machstep}^T$ is a complete abstraction of $\widehat{\machstep}$.
\end{theorem}
The proof follows from the Galois connection that, in one direction,
sorts all the stores in $S$ to form $\Sigma$, and translates stores in
$S$ to their distance from the end of $\Sigma$ (their timestamp). In the other
direction, timestamps in $S$ are replaced by the stores they point to in $\Sigma$.
